Flow-Based Cost Allocation in Linear Optimized Power Systems are non-unique but localizable

### 2020-08-17 paper/flow_based.tex
make price adjustment flexible

In more realistic setups, generators, lines or other assets can only be built up to a certain limit. This might caused by land use restrictions or social acceptance problems. %In the following give a general solution how the cost allocation may handle this.  
However, when constraining the capacity $\capacity$  for a subset $I$ of assets to an upper limit,
\begin{align}
    \capacity - \capacityupper \le 0 \resultsin{\muuppernom} \hpad \Forall{i \in I}
\label{eq:capacityexpansionmaximum}
\end{align}
the zero profit condition for asset $i$ alters and the revenues don't match the expenditures anymore. More precisely, the revenue from the shadow prices given in \cref{tab:cost_allocation_map} exceed the CAPEX $\cost_i$ by $\remainingcost_i$, thus  
\begin{align}
 \cost_i - \remainingcost_i =  \sum_t \costfactor \, \state \Forall{i}
 \label{eq:capex_generation_duality_bf2}
\end{align}
where the difference is given by 
\begin{align}
    \remainingcost_i = - \muuppernom \capacity
    \Forall{i}
\end{align}
In order to take this effect into account for the cost allocation, we update the cost factors in \cref{tab:cost_allocation_map} to

\begin{align}
    \costfactor \rightarrow \dfrac{c_i}{c_i + \muuppergenerationnom}\, \costfactor
\end{align}
This ensures that the allocated CAPEX sum up to the actual CAPEX at asset $i$ (and \cref{eq:cost_payback} holds).

@@

In order to take already built infrastructure into account, the capacity $\capacity$ can be constrained to a minimum required capacity $\capacitylower$. Mathematically this translates to 
\begin{align}
    \capacitylower - \capacity  \le 0 \resultsin{\mulowernom} \hpad \forall{i \in I}
\label{eq:capacityexpansionminimum}
\end{align}
Again, such a setup alters the zero profit condition of asset $i$ as soon as the constraint becomes binding. 
In that case, asset $i$ does not collect enough revenue in order to match the CAPEX. The difference is given by 
\begin{align}
    \remainingcost_i = \mulowernom \capacity
    \Forall{i}
\end{align}
Again, we can balance this effect out by updating the cost factor to 
\begin{align}
    \costfactor \rightarrow \costfactor + 
\end{align}

>>>>

In more realistic setups, generators, lines or other assets can only be built up to a certain limit. This might caused by land use restrictions or social acceptance problems. %In the following give a general solution how the cost allocation may handle this.  
However, when constraining the capacity $\capacity$  for a subset $I$ of assets to an upper limit,
\begin{align}
    \capacity - \capacityupper \le 0 \resultsin{\muuppernom} \hpad \Forall{i \in I}
\label{eq:capacityexpansionmaximum}
\end{align}
the zero profit condition for asset $i$ alters. Then the revenues don't match the expenditures as soon as the constraint becomes binding. More precisely, the revenue from the shadow prices given in \cref{tab:cost_allocation_map} exceed the CAPEX $\cost_i$ by $\remainingcost_i$,  where  $\remainingcost_i$ is given by
\begin{align}
    \remainingcost_i = - \muuppernom \capacity
    \Forall{i}
\end{align}
% \begin{align}
%  \cost_i - \remainingcost_i =  \sum_t \costfactor \, \state \Forall{i}
%  \label{eq:capex_generation_duality_bf2}
% \end{align}
For the cost allocation, these means the prices in \cref{tab:cost_allocation_map} have to be adjusted, as otherwise consumers would pay too much. As we show in ... updating the prices by a fix ratio 
\begin{align}
    \costfactor \rightarrow \dfrac{c_i}{c_i + \muuppernom}\, \costfactor
    \label{eq:adjustment_lowernom}
\end{align}
will ensure that the allocated CAPEX sum up to the actual CAPEX at asset $i$, meaning that \cref{eq:cost_payback} holds. Note that $\muuppernom$ is a positive number, so the adjustment cannot increase the paid price.

@@

In order to take already built infrastructure into account, the capacity $\capacity$ can be constrained to a minimum required capacity $\capacitylower$. Mathematically this translates to 
\begin{align}
    \capacitylower - \capacity  \le 0 \resultsin{\mulowernom} \hpad \forall{i \in I}
\label{eq:capacityexpansionminimum}
\end{align}
Again, such a setup alters the zero profit condition of asset $i$, as soon as the constraint becomes binding. 
In that case, asset $i$ does not collect enough revenue in order to match the CAPEX. The difference is given by 
\begin{align}
    \remainingcost_i = \mulowernom \capacity
    \Forall{i}
\end{align}
In constrast to 
Again, we can balance this effect out by updating the cost factor to 
\begin{align}
    \costfactor \rightarrow \costfactor +  \dfrac{\mulowernom \capacity}{\sum_t \state}
\end{align}
As $\mulowernom$ is a positive number, this will increase the price and therefore the revenue for asset $i$.
